Kids PM Summary

### 2020-07-24 lrti_tracking.Rmd
lrti data update

```{r}
health_exposure_data_sampling_day <- read_rds("Output/health_exposure_data_sampling_day.rds")
```

@@

```{r}
# LRTI Diagnosis data
lrti_diagnosis_data <- health_exposure_data_sampling_day %>% 
  # select relevant health data
  select(area, home, home_winter_id, winter_id, child_id_num, 
         visit_date, med_visit_date, med_visit_referred,
         csq_date:csq_symptom_free_date,
         csq_see_dr, csq_dr_diagnosis,
         med_rec_visit_date:med_rec_comments,
         csq_miss_work:csq_comments,
         med_visit_ari:med_visit_mean_temp,
         lrti_number:lrti_professional_comments) %>% 
  # Currently only have this data for WMT - need to get new files and updates dataset
  filter(area == "WMT") %>% 
  # This is the most broad way of distinguishing if a child was sick
  # Careful when filtering here. Could still make cases that these vars didn't catch
  # Best to have a look through all rows, then use this to filter data down so it
  # is easier to work with to assess dates/at-risk times
  filter(csq_sick_2_weeks == "Yes" | csq_still_sick == "Yes") %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  ungroup()

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds"))

health_data_merged <- 
  read_rds(paste0(file_path, "Output/health_data_merged.rds"))

wmt_chw <- read_xlsx(paste0(file_path, "input/WMT/childhomewinter.xlsx")) %>% 
  mutate(area = "WMT") %>% 
  rename(paul_comments = 19)
nn_chw <- read_xlsx(paste0(file_path, "input/NN/childhomewinter.xlsx")) %>% 
  mutate(area = "NN") %>% 
  rename(paul_comments = 19)
ak_chw <- read_xlsx(paste0(file_path, "input/AK/childhomewinter.xlsx")) %>% 
  mutate(area = "AK") %>% 
  rename(paul_comments = 19)

child_home_winter <- rbind(wmt_chw, nn_chw, ak_chw) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         paul_lrti = AnyARI) %>% 
  select(area, home_winter_id, child_id_num, paul_lrti, paul_comments) %>% 
  filter(paul_lrti %in% c("Yes", "Debating"))

demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds")) %>% 
  select(child_id_num, child_id_char, area, winter_id)
```

@@

```{r}
# LRTI Diagnosis data
lrti_diagnosis_data <- health_data_merged %>% 
  # select relevant health data
  select(area, home, home_winter_id, winter_id, child_id_num, 
         visit_date, csq_date:sibling_school, treatment_assigned) %>% 
  filter(!is.na(visit_date)) %>% 
  full_join(child_home_winter, by = c("area", "home_winter_id", "child_id_num")) %>% 
  filter(home_winter_id == 19)
  # This is the most broad way of distinguishing if a child was sick
  # Careful when filtering here. Could still make cases that these vars didn't catch
  # Best to have a look through all rows, then use this to filter data down so it
  # is easier to work with to assess dates/at-risk times
  filter(csq_sick_2_weeks == "Yes" | csq_still_sick == "Yes") %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  ungroup()

### 2020-07-24 pm_summary.Rmd
lrti data update

```{r, fig.height=4, fig.width=3}
boxplots_kids_pm <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(area, pm_mean_sampling_period)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    theme_minimal() +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm

>>>>

```{r, fig.height=4, fig.width=3}
boxplots_kids_pm <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(area, pm_mean_sampling_period)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    theme_minimal() +
    labs(title = "Red triangle = mean",
         y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
